\section{Optimal constraint ratio for shear locking}
The previous section has been mentioned that the shear locking is consisted of two parts, shear force locking and shear strain locking.
The corresponding LBB conditions are listed as follows:
\begin{itemize}
    \item Shear force locking LBB condition:
        \begin{equation}\label{eq:LBB_q}
        \inf_{w_h\in W_h} \sup_{\boldsymbol q_h \in Q_h} \frac{\vert b_w(w_h,\boldsymbol q_h)\vert}{\Vert w_h\Vert_W \Vert \boldsymbol q_h \Vert_Q} \ge \beta_q
        \end{equation}
    \item Shear strain locking LBB condition:
        \begin{equation}\label{eq:LBB_gamma}
        \inf_{\boldsymbol q_h \in Q_h} \sup_{\boldsymbol u_h \in W_h \times \Phi_h}
        \frac{\vert b(\boldsymbol q_h, \boldsymbol u_h) \vert}{\Vert \boldsymbol q_h \Vert_Q \Vert \boldsymbol u_h \Vert_{W\times \Phi}} \ge \beta_\gamma
        \end{equation}
\end{itemize}
where, $\beta_q$ and $\beta_\gamma$ are LBB coefficients. The norms in the above LBB conditions are defined as follows:
\begin{align}
\Vert w_h \Vert_W^2 &= \int_\Omega \delta w_h kGh  w_h d\Omega \\
\Vert \boldsymbol q_h \Vert_Q^2 &= 
\int_\Omega \frac{\delta \boldsymbol q_h \cdot \boldsymbol q_h}{kGt} d\Omega \\
\Vert \boldsymbol \varphi_h \Vert_\Phi^2 &= 
\int_\Omega \delta \boldsymbol \kappa_h : \frac{t^3}{12} \boldsymbol D : \boldsymbol \kappa_h d\Omega \\
\Vert \boldsymbol u_h \Vert_{W\times\Phi}^2 &= 
\Vert w_h \Vert_W^2 + \Vert \boldsymbol \varphi_h \Vert_\Phi^2
\end{align}
Next, we will focus on these two LBB conditions respectively and employ the complete-polynormial-based estimate method \cite{wu2026} to investigate the relationship between their LBB coefficients $\beta_q$ and $\beta_\gamma$ and the degree of freedoms (DOFs) for variables $w_h$, $\boldsymbol \varphi_h$ and $\boldsymbol q_h$.
The detailed path for the complete-polynormial-based estimate method is lised in \ref{sec:estimator}.
Consequently, the optimal ratio of degrees of freedoms (DOFs) between variables can be revealed based on these two estimators.

\subsection{Estimator for $\beta_q$}
The coefficient $\beta_q$ controls the behavior of shear force locking in Eq. \eqref{eq:force_locking_weak}, the detailed enforcement is listed as follows:
\begin{equation}
    \begin{aligned}
        &b_w(\delta w_h, \boldsymbol q_h) - f_w(\delta w_h) = (\delta w_h, \mathcal W \boldsymbol q_h) - f_w(\delta w_h) \\
        =& \int_{\Gamma_q} \delta w_h(\boldsymbol q_h \cdot \boldsymbol n - \bar q_n) d\Gamma - \int_\Omega \delta w_h (\nabla \cdot \boldsymbol q_h + \bar p) d\Omega \\
        =& 0
    \end{aligned}
\end{equation}
where, the constraints includes two parts, one is the equilibrium equation between shear force resultant and  transverse load in $\Omega$, the other is the natrual shear force boundary condition on $\Gamma_q$.
In accordance with the general form of completed-polynormial-based estimator mentioned in \ref{sec:estimator}, 
the operator $\mathcal W: Q\rightarrow W$ is a specific instance of $\mathcal P$ in Theorem.\ref{thm:estimator}, and is defined as:
\begin{equation}\label{eq:operator_W}
\mathcal W = \left \{
    \begin{aligned}
        &\mathcal W^\Omega = -\nabla \cdot & & \textrm{in}\; \Omega \\
        &\mathcal W^{\Gamma_q}\mathcal T^{\Gamma_q}, \; \mathcal W^{\Gamma_q} = \boldsymbol n \cdot & & \textrm{on}\; \Gamma_q
    \end{aligned}
    \right .
\end{equation}
where, based on the trace theorem \cite{}, $\mathcal T^{\Gamma_q}: Q \rightarrow Q\vert_{\Gamma_q}$ is a trace operator mapping the shear force $\boldsymbol q$ from domain $\Omega$ to the boundary $\Gamma_q$, while the parametric variable of $\boldsymbol q$ on boundary can be represented using $s$, i.e. $\boldsymbol q(s) \in Q\vert_{\Gamma_q}$. 
According to Theorem.\ref{thm:estimator}, the completed-polynomial-based estimator of $\beta_q$ has the following form:
\begin{equation}\label{eq:beta_q}
\beta_q \le \inf_{Q'\subset Q_{n_q} \setminus \ker \mathcal W_h \mathcal I_h^q}
\sup_{\boldsymbol q \in Q'}
\frac{\Vert \mathcal W\boldsymbol q \Vert_W}{\Vert \boldsymbol q \Vert_Q} + O(h)
\end{equation}
in which $\mathcal I_h^q:Q_{n_q}\rightarrow Q_h$ is the interpolation operator for shear force resultant.
$\mathcal W_h:Q_h\rightarrow W_h$ is the orthogonal operator of $\mathcal W$, i.e. $(\delta w_h, \mathcal W \boldsymbol q_h - \mathcal W_h \boldsymbol q_h)=0$.
$Q_{n_q}\subset Q$ is the polynomial space that has the identical dimensions with $Q_h$, i.e. $\dim Q_{n_q} = \dim Q_h = 2n_q$.

From Eq. \eqref{eq:beta_q}, the LBB condition of Eq. \eqref{eq:LBB_q} can be maintained while the first term on right-hand side of Eq. \eqref{eq:beta_q} is non-zero, which should be necessarily required that:
\begin{equation}\label{eq:dim_relation_1}
    \dim \left(Q_{n_q} \setminus \ker \mathcal W_h \mathcal I_h^q\right) \le \dim \left(Q_{n_q} \setminus \ker \mathcal W\right)
\end{equation}
where, obviously, leading the definitions of $\mathcal I_h^q$ and $Q_{n_q}$, and the rank--nullity theorem, the left-hand side of Eq. \eqref{eq:dim_relation_1} can be rewritten as:
\begin{equation}\label{eq:dim_relation_2}
    \begin{split}
        \dim \left(Q_{n_q} \setminus \ker \mathcal W_h \mathcal I_h^q\right) &= \dim \left(Q_h\setminus \ker \mathcal W_h\right) \\
        &= \dim Q_h - \dim \left(\ker \mathcal W_h\right) \\
        &= \dim(\mathrm{Im} \mathcal W_h) \\
        &= \dim W_h = n_w
    \end{split}
\end{equation}

In contrast, to evaluate the right--hand side of Eq. \eqref{eq:dim_relation_1}, we first introduce the definition of operator $\mathcal W$ in \eqref{eq:operator_W}, $\ker \mathcal W$ can be represented as:
\begin{equation}\label{eq:space_W}
    \ker \mathcal W = \ker \mathcal W^\Omega \cap \ker \mathcal W^{\Gamma_q} \mathcal T^{\Gamma_q}
\end{equation}
According to above equation, the space $Q_{n_q}\setminus \ker \mathcal W$ can be expressed by two terms,
one is regarding the kernel space of $\mathcal W^\Omega$, the other is regarding the kernel space of $\mathcal W^{\Gamma_q}\mathcal T^{\Gamma_q}$, yields:
\begin{equation}\label{eq:dim_relation_3}
    \begin{split}
        \dim(Q_{n_q}\setminus\ker\mathcal W)
        &=\dim \left(Q_{n_q}\setminus (\ker\mathcal W^\Omega\cap\ker\mathcal W^{\Gamma_q}\mathcal T^{\Gamma_q})\right) \\
        &=\dim\left(Q_{n_q} \setminus \ker \mathcal W^\Omega\right)
        \cup 
        \dim\left(Q_{n_q}\setminus \ker \mathcal W^{\Gamma_q}\mathcal T^{\Gamma_q}\right) \\
        &= \dim\left(Q_{n_q}\setminus\ker \mathcal W^\Omega\right)
        +\dim\left(Q_{n_q}\setminus \ker \mathcal W^{\Gamma_q}\mathcal T^{\Gamma_q}\right) \\
        &-\dim\left((Q_{n_q}\setminus\ker \mathcal W^\Omega)\cap (Q_{n_q}\setminus \ker \mathcal W^{\Gamma_q}\mathcal T^{\Gamma_q})\right)
    \end{split}
\end{equation}
where the second and third equations of Eq. \eqref{eq:dim_relation_3} is derived based on De Morgan's theorem\cite{} and Grassmann's theorem\cite{} respectively.
For clarity, these two theorems are illustrated in \ref{sec:functional}.

For the first term regarding the kernel space of $\mathcal W^\Omega$,
in accordance with rank--nullity theorem\cite{strang2006}, the dimension of this space is equal to the that of the image space of $\mathcal W^\Omega$ as:
\begin{equation}
    \dim \left(Q_{n_q}\setminus \ker \mathcal W^\Omega\right) = \dim Q_{n_q} - \dim\left(\ker \mathcal W^\Omega\right) = \dim \left(\mathrm{Im} \mathcal W^\Omega\right)
\end{equation}
Because of the $Q_{n_q}$ is the second order polynomial tensor space with dimension of $2n_q$
and the $\mathcal W^\Omega$ is the divergence operator acting on $Q_{n_q}$, the polynomial in $\mathrm{Im} \mathcal W^\Omega$ is one order lower than polynomial order of $Q_{n_q}$.
The following equation presents the detailed monomial basis of $Q_{n_q}$, and the kernel space of operator $\mathcal W^\Omega$:
\begin{equation}
    Q_{n_q} = \mathrm{span} \left \{
        \underbrace{
        \begin{pmatrix}
            1 \\ 0
        \end{pmatrix},
        \begin{pmatrix}
            0 \\ 1
        \end{pmatrix},
        \begin{pmatrix}
            y \\ 0
        \end{pmatrix},
        \begin{pmatrix}
            0 \\ x
        \end{pmatrix},
        \begin{pmatrix}
            x \\ -y
        \end{pmatrix},
        \dots}_{\ker \mathcal W^\Omega}, 
        \underbrace{
        \begin{pmatrix}
            x \\ y
        \end{pmatrix},
        \dots}_{Q_{n_q}\setminus \ker \mathcal W^\Omega}
    \right \}
\end{equation}

To simplify the expression, we define two operators to implement the transformation between the order of a complete polynomial space, namely $n_o$ and its monomial basis number, namely $n_m$:
\begin{equation}
n_o = [n_p] = \frac{\sqrt{1+8n_p}-3}{2}
,\quad
n_p = \langle n_o \rangle = \frac{(n_o+1)(n_o+2)}{2}
\end{equation}
where $\langle [n] \rangle = n$.
Therefore, the dimension of $\mathrm{Im} \mathcal W^\Omega$ can be estimated by:
\begin{equation}\label{eq:dim_relation_3_1}
    \langle \lfloor [n_q] \rfloor - 1\rangle \le \dim(\mathrm{Im} \mathcal W^\Omega) \le \langle \lceil [n_q] \rceil -1 \rangle
\end{equation}
in which $\lfloor\bullet\rfloor$ and $\lceil\bullet\rceil$ are the floor and ceiling functions, respectively.


For the second term regarding the kernel space of $\mathcal W^{\Gamma_q} \mathcal T^{\Gamma_q}$, leading the Lemma.\ref{lma:trace} listed in \ref{sec:functional}, the dimension of $Q_{n_q}\setminus\ker \mathcal W^{\Gamma_q}\mathcal T^{\Gamma_q}$ becomes:
\begin{equation}\label{eq:dim_relation_3_2_1}
    \begin{aligned}
        \dim\left(Q_{n_q}\setminus\ker \mathcal W^{\Gamma_q}\mathcal T^{\Gamma_q}\right)&=
        \dim\left(Q_{n_q^{\Gamma}}\setminus\ker \mathcal W^{\Gamma_q}\right) \\
        &= \dim Q_{n_q^{\Gamma}} - \dim\left(\ker \mathcal W^{\Gamma_q}\right) \\
        &= \dim(\mathrm{Im}\mathcal W^{\Gamma_q})
    \end{aligned}
\end{equation}
where $Q_{n_q^\Gamma}\subset Q\vert_{\Gamma_q}$ is the polynomial space with the identical dimension of trace space $\mathcal T^{\Gamma_q}(Q_h)$,
i.e. $\dim Q_{n_q^\Gamma} = \dim \mathcal T^{\Gamma_q}(Q_h) = 2n_q^\Gamma$.
For instance, the detailed monomial basis of $Q_{n_q^\Gamma}$ is listed as follows:
\begin{equation}\label{eq:Q_n_q_gamma}
    Q_{n_q^\Gamma} = \mathrm{span} \left \{
        \underbrace{
        \begin{pmatrix}
            n_2 \\ -n_1
        \end{pmatrix},
        \begin{pmatrix}
            n_2 s \\ -n_1 s
        \end{pmatrix},
        \begin{pmatrix}
            n_2 s^2 \\ -n_1 s^2
        \end{pmatrix},
        \dots}_{\ker \mathcal W^{\Gamma_q}},
        \underbrace{
        \begin{pmatrix}
            n_2 \\ n_1
        \end{pmatrix},
        \begin{pmatrix}
            n_2 s \\ n_1 s
        \end{pmatrix},
        \begin{pmatrix}
            n_2 s^2 \\ n_1 s^2
        \end{pmatrix},
        \dots}_{Q_{n_q}^\Gamma\setminus \ker \mathcal W^{\Gamma_q}}
    \right \}
\end{equation}
It is clear that, from Eq. \eqref{eq:Q_n_q_gamma}, the dimension of second term is evaluated as:
\begin{equation}\label{eq:dim_relation_3_2}
    \dim\left(Q_{n_q}\setminus\ker \mathcal W^{\Gamma_q}\mathcal T^{\Gamma_q}\right) = n_q^\Gamma
\end{equation}

With the consideration of Eqs. \eqref{eq:dim_relation_3}, \eqref{eq:dim_relation_3_1} and \eqref{eq:dim_relation_3_2}, the right-hand side of Eq. \eqref{eq:dim_relation_1} becomes to:
\begin{equation}\label{eq:dim_relation_4}
\max(\langle\lfloor[n_q]\rfloor-1\rangle,n_q^\Gamma)
\le\dim(Q_{n_q}\setminus\ker\mathcal W)\le
\langle\lceil[n_q]\rceil-1\rangle + n_q^\Gamma
\end{equation}

It is noted that the dimension of the trace space $\mathcal T^{\Gamma_q}(Q_h)$ is generally identical to the number of DOFs on $\Gamma_q$, i.g. for finite element approximation.
So generally speaking, $n_q^\Gamma \ll \langle\lfloor[n_q]\rfloor-1\rangle$.
To totally ensure the LBB condition of Eq. \eqref{eq:LBB_q}, considering Eqs. \eqref{eq:dim_relation_1}, \eqref{eq:dim_relation_2} and \eqref{eq:dim_relation_4}, the $n_w$ should be always less than the low bound of $Q_{n_q}\setminus\ker\mathcal W$'s dimension, i.e.:  
\begin{equation}\label{eq:dim_relation_5}
    n_w \le \langle\lfloor[n_q]\rfloor-1\rangle
\end{equation}



\subsection{Estimator for $\beta_\gamma$}
The behavior of shear strain locking in Eq. \eqref{eq:LBB_gamma} is controlled by the coefficient $\beta_\Gamma$, where the shear strain locking contains two parts as follows: 
\begin{equation}
    \begin{aligned}
        &b(\delta \boldsymbol q_h, \boldsymbol u_h) - f_q(\delta \boldsymbol q_h)  = (\delta \boldsymbol q_h, \mathcal Q \boldsymbol u_h) - f_q(\delta \boldsymbol q_h)\\
        =& \int_\Omega \delta \boldsymbol q \cdot (\nabla w - \boldsymbol \varphi) d\Omega - \int_{\Gamma_w} \delta \boldsymbol q \cdot \boldsymbol n (w-\bar w)d\Gamma \\
        =& 0
    \end{aligned}
\end{equation}
where the product operator herein stands for the tensors. And the operator $\mathcal Q:W\times\Phi\rightarrow Q$ is defined individually in the domain $\Omega$ and on the boundary $\Gamma_w$ by:
\begin{equation}\label{eq:mathcal_Q}
\mathcal Q = \left\{
    \begin{aligned}
        &\mathcal Q^\Omega = \{\nabla, -\} & & \text{in}\;\Omega \\
        &\mathcal Q^{\Gamma_w}\mathcal T^w, \;\mathcal Q^{\Gamma_w} = -\boldsymbol n & & \text{on}\;\Gamma_w
    \end{aligned}
\right.
\end{equation}
in which, in accordance with trace theorem \cite{}, $\mathcal T^w:W\times\Phi\rightarrow W\vert_{\Gamma_w}$ is the trace operator mapping displacement $\boldsymbol u$ from domain $\Omega$ to boundary $\Gamma_w$. 
Again, introducing the Theorem. \ref{thm:estimator}, the $\beta_\gamma$ can further be bounded by:
\begin{equation}\label{eq:beta_gamma}
\beta_\gamma\le\inf_{U'\subset W_{n_w}\times \Phi_{n_\varphi}\setminus \ker \mathcal Q_h\mathcal I_h^u} \sup_{\boldsymbol u_h \in U'}
\frac{\Vert \mathcal Q \boldsymbol u\Vert_Q}{\Vert \boldsymbol u \Vert_{W\times \Phi}} + O(h)
\end{equation}
where $\mathcal I_h^u: W_{n_w}\times\Phi_{n_\varphi}\rightarrow W_h\times\Phi_h$ is the interpolation operator for deflection $w$ and rotation $\boldsymbol \varphi$, 
and $W_{n_w}$, $\Phi_{n_\varphi}$ are the polynomial spaces that have the identical dimensions with $W_h$, $\Phi_h$ respectively,
i.e. $\dim W_{n_w} = \dim W_h = n_w$, $\dim \Phi_{n_\varphi} = \dim \Phi_h = 2n_\varphi$.

To maintain the LBB condition of \eqref{eq:LBB_gamma}, i.e. $\beta_\gamma$ is a coefficient independent with characterized length $h$, the dimensions of the relative spaces in Eq. \eqref{eq:beta_gamma} should satisfy the following relationship:
\begin{equation}\label{eq:dim_relation_6}
\dim \left(W_{n_w}\times\Phi_{n_\varphi}\setminus\ker\mathcal Q_h \mathcal I_h^u\right) \le
\dim \left(W_{n_w}\times\Phi_{n_\varphi}\setminus\ker\mathcal Q\right)
\end{equation}
The left-hand side of Eq. \eqref{eq:dim_relation_6} can be represented by the DOFs of approximated shear force resultant:
\begin{equation}
    \begin{split}
        \dim \left(W_{n_w}\times \Phi_{n_\varphi}\setminus\ker\mathcal Q_h\mathcal I_h^u\right)
        &= \dim \left(W_h\times \Phi_h\setminus\ker\mathcal Q_h\right) \\
        &= \dim(W_h\times\Phi_h) - \dim(\ker \mathcal Q_h) \\
        &= \dim(\mathrm{Im} \mathcal Q_h) \\
        &= \dim Q_h = 2n_q
    \end{split}
\end{equation}

On the other hand, with De Morgan's theorem and Grassmann's theorem \cite{}, the right-hand side of Eq. \eqref{eq:dim_relation_6} becomes:
\begin{equation}\label{eq:dim_relation_7}
    \begin{split}
        &\dim(W_{n_w}\times\Phi_{n_\varphi}\setminus\ker\mathcal Q) \\
        =&\dim \left(W_{n_w}\times\Phi_{n_\varphi}\setminus (\ker\mathcal Q^\Omega\cap\ker\mathcal Q^{\Gamma_w}\mathcal T^{\Gamma_w})\right) \\
        =&\dim\left(W_{n_w}\times\Phi_{n_\varphi} \setminus \ker \mathcal Q^\Omega\right)
        \cup 
        \dim\left(W_{n_w}\times\Phi_{n_\varphi}\setminus \ker \mathcal Q^{\Gamma_w}\mathcal T^{\Gamma_w}\right) \\
        =& \dim\left(W_{n_w}\times\Phi_{n_\varphi}\setminus\ker \mathcal Q^\Omega\right)
        +\dim\left(W_{n_w}\times\Phi_{n_\varphi}\setminus \ker \mathcal Q^{\Gamma_w}\mathcal T^{\Gamma_w}\right) \\
        -&\dim\left((W_{n_w}\times\Phi_{n_\varphi}\setminus\ker \mathcal Q^\Omega)\cap (W_{n_w}\times\Phi_{n_\varphi}\setminus \ker \mathcal Q^{\Gamma_w}\mathcal T^{\Gamma_w})\right)
    \end{split}
\end{equation}
where the relationship of $\ker \mathcal Q = \ker \mathcal Q^\Omega \cap \ker \mathcal Q^{\Gamma_w}\mathcal T^{\Gamma_w}$ is used herein.
Similarly, this dimension of Eq. \eqref{eq:dim_relation_7} is consisted of two terms, one relates to the kernel space of $\mathcal Q^\Omega$ in $\Omega$, the other relates to the kernel space of $\mathcal Q^{\Gamma_w}\mathcal T^w$ on $\Gamma_w$.

The dimension of first term regarding the kernel space of $\mathcal Q^\Omega$ can be revealed by the detailed expression of monomial basis of $W_{n_w}\times \Phi_{n_\varphi}$ as:
\begin{equation}
W_{n_w}\times \Phi_{n_\varphi} = \mathrm{span} \left \{\begin{split}
&\overbrace{
\begin{pmatrix}
1 \\ 0 \\ 0
\end{pmatrix},
\begin{pmatrix}
x \\ 1 \\ 0
\end{pmatrix},
\begin{pmatrix}
y \\ 0 \\ 1
\end{pmatrix},
\begin{pmatrix}
x^2 \\ 2x \\ 0
\end{pmatrix},
\begin{pmatrix}
xy \\ y \\ x
\end{pmatrix},
\begin{pmatrix}
y^2 \\ 0 \\ 2y
\end{pmatrix},
\dots}^{\ker \mathcal Q^\Omega}, \\
&\underbrace{
\begin{pmatrix}
0 \\ 1 \\ 0
\end{pmatrix},
\begin{pmatrix}
0 \\ 0 \\ 1
\end{pmatrix},
\begin{pmatrix}
0 \\ x \\ 0
\end{pmatrix},
\begin{pmatrix}
0 \\ 0 \\ x
\end{pmatrix},
\begin{pmatrix}
0 \\ y \\ 0
\end{pmatrix},
\begin{pmatrix}
0 \\ 0 \\ y
\end{pmatrix},
\dots}_{W_{n_w}\times\Phi_{n_\varphi}\setminus \ker Q^\Omega}
\end{split}\right \}
\end{equation}
Obviously, the monomial basis of deflection $w$ is one order higher than that of rotation in $\ker \mathcal Q^\Omega$.
So the dimension of $\ker \mathcal Q^\Omega$ can be evaluated by:
\begin{equation}
\dim \ker \mathcal Q^\Omega = \min (n_w,n_s)
\end{equation}
with
\begin{equation}
\langle \lfloor [n_\varphi] \rfloor+1 \rangle \le n_s \le \langle \lceil[n_\varphi]\rceil + 1 \rangle
\end{equation}
where $n_w$ presents the number of monomial basis for $w$. $n_s$ stands for the monomial basis number with one order higher than $\Phi_{n_\varphi}$'s monomial basis.
Then, the dimension of $W_{n_w}\times\Phi_{n_\varphi}\setminus\ker \mathcal Q^\Omega$ can be evaluated by: 
\begin{equation}\label{eq:dim_relation_8}
    \begin{split}
        \dim\left(W_{n_w}\times\Phi_{n_\varphi}\setminus\ker \mathcal Q^\Omega\right) &= \dim\left(W_{n_w}\times\Phi_{n_\varphi}\right) - \dim\left(\ker \mathcal Q^\Omega\right) \\
        &=n_w + 2n_\varphi - \min (n_w,n_s)
    \end{split}
\end{equation}

To further calculate the dimension of the second term regarding the kernel space of $\mathcal Q^{\Gamma_w}\mathcal T^{\Gamma_w}$, we first suppose the trace space $\mathcal T^{\Gamma_w}(W_h\times\Phi_h)$ and its corresponding polynomial space $W_{n_w^\Gamma}$, $\dim W_{n_w^\Gamma}=\dim \mathcal T^{\Gamma_w}(W_h\times\Phi_h)=n_w^\Gamma$.
Using the Lemma.\ref{lma:trace} in \ref{sec:functional}, we have:
\begin{equation}\label{eq:dim_relation_9}
    \begin{split}
        \dim\left(W_{n_w}\times\Phi_{n_\varphi}\setminus\ker\mathcal Q^{\Gamma_w}\mathcal T^{\Gamma_w}\right)
        &= \dim \left(W_{n_w^\Gamma}\setminus \ker \mathcal Q^{\Gamma_w}\right) \\
        &= \dim W_{n_w^\Gamma} - \underbrace{\dim \left( \ker \mathcal Q^{\Gamma_w}\right)}_0 \\
        &= \dim W_{n_w^\Gamma} = n_w^\Gamma \\
    \end{split}
\end{equation}
where, it can reveal from the expression of $\mathcal Q^{\Gamma_w}$ in Eq.\eqref{eq:mathcal_Q} that, the space $\ker \mathcal Q^{\Gamma^w}$ is empty, i.e $\dim(\ker \mathcal Q^{\Gamma^w} = 0$). 

Consequently, substituting Eqs.\eqref{eq:dim_relation_8} and \eqref{eq:dim_relation_9} into Eq.\eqref{eq:dim_relation_7}, the right-hand side of Eq.\eqref{eq:dim_relation_6} can be rewritten as:
\begin{multline}
    \max(n_w + 2n_\varphi - \min (n_w,n_s),n_w^\Gamma) \le
    \dim\left(W_{n_w}\times\Phi_{n_\varphi}\setminus\ker\mathcal Q\right) \\ \le
    n_w + 2n_\varphi - \min (n_w,n_s) + n_w^\Gamma
\end{multline}
It is clear that $n_w^\Gamma \ll n_w + 2n_\varphi - \min (n_w,n_s)$ 
FIXME

\begin{equation}
n_q \le n_\varphi
\end{equation}
\begin{equation}
    n_w^{\mathrm{opt}} = \langle\lfloor[n_q]\rfloor-1\rangle
    ,\quad
    n_q^{\mathrm{opt}} = n_\varphi
\end{equation}

\begin{rmk}
It should be noted that, the proposed estimator is considered for the entire domain and all the nodal discretization should be so well-pose that the monomial basis number of equivalent polynomial space is equal to the degree of freedoms for approximation space, i.g $\dim W_{n_w} = \dim W_h = n_w$.
While a local domain contains a too dense nodal distribution than others, the nodal discretization satisfied the estimator will still meet the locking issue in local.
\end{rmk}